### 2016-08-31 version0.0/intro0.01.tex
Changing MHz to J

%ISM 1)Gas 2)dust
%There could be a galaxy without stars (i.e. dark galaxies~\citep[][and references therein]{Cantalupo12}), but there will never be a galaxy without gas. %: this is a very strong statement. Some galaxies, like dwarf ellipticals, are pretty gas-free (at least now). So qualify this a bit. done
Among observable objects in galaxies, gas has a crucial role in formation and evolution of galaxies.
Gas and dust in galaxies can be found in the space between stars.
This space is called the interstellar medium (ISM), and is full of low density gaseous clouds with neutral or ionized atoms and/or molecules, and microscopic dust grains.
The gas and dust in the ISM are heated by interstellar radiation field and cooled through a variety of line and continuum processes which usually depend on the local physical conditions. 
The effect of the ISM on stellar formation is undeniable; it provides the raw material for the formation of stars~\citep[e.g.][]{Kennicutt08,Bigiel08}.
Studying the interstellar medium is not only essential to understanding the formation of stars, but is also  necessary for interpretation of stellar evolution due to fact that stars release their material into ISM when they reach the end of their evolutionary track.

@@

The molecular clouds are surrounded by clouds of atomic gas~\citep{Kennicutt12}, which are easily traceable by 21-cm emission.
Hydrogen atoms in the ISM (excluding the regions close to hot stars, see below) are in their ground state, which is the state of lowest energy.
Due to a coupling between the total angular momentum of the electron and the angular momentum (spin) of the nucleus, the ground state of hydrogen atom splits into two states that are separated in energy by an amount of 1420.40~MHz.
This splitting is referred to as the hyperfine structure. 
The electron can be in either of the two aforementioned states. 
These states are very stable and the transition between them is forbidden, with a transition rate of $2.5\times10^{-15}\mathrm{s}^{-1}$.
This means that one would expect this transition to naturally happen once every ten million years.
%The electron and proton spins in the ground state can be parallel (i.e. both spin up) or anti-parallel (i.e. the proton's spin is up and the electron's spin is down or vice versa). 
%The energy of the anti-parallel mode is slightly less than the parallel mode.
%Since atoms always tend to be in the state with lowest energy possible, electrons in the parallel mode have a tendency to flip to the anti-parallel mode. 
%However, the energy difference between these two states is very small and it takes millions of years before the transition happens.
However, the large amounts of hydrogen atoms in these atomic clouds compensate for the rarity of the transition and at any given time, there are enough hydrogen atoms to emit the 21-cm radiation. 
Observation of the \hi~atoms is specifically necessary for understanding physical properties and dynamics of the ISM, which leads to understanding the star formation process~\citep{Walter08}.

@@

Dust has an insignificant effect on the mass of the ISM, but it plays crucial roles in the ISM's evolution.
In spiral galaxies, dust grains are located in cold regions ($\sim$30~K) and empirically proven that they have a power-law size distribution.
The source of energy for dust thermal emission is heating from stars, and the shape of the continuum depends on size of the grain.
Mid-infrared emission from dust grains is mainly dominated by PAHs heated by evolved stellar population~\citep{Smith07a} or recently formed intermediate-mass young stars~\citep{Peeters04}.
Large grains that are either heated by light from star-forming regions or by the interstellar radiation field from the total stellar population emit most of their light in far-infrared~\citep[e.g.][]{Calapa14, lu14}
Dust is the main source of extinction and reddening of starlight (see Sec.\ref{sec: extinction} for more information).

@@

Extinction happens when there is a combination of both absorption and scattering of radiation by dust.
This effect grows inversely with wavelength.
%Extinction can be defined as a reduction of the original intensity caused by dust:
Extinction is quantified as the difference in observed and initial magnitudes of an object in a specific wavelength ($\lambda$):
\begin{equation}
m_{\lambda} - m_{\lambda}(0) = \mathrm{A}_{\lambda},
\end{equation}
where $\mathrm{A}_{\lambda}$ is the extinction, and $m_{\lambda}$ and $m_{\lambda}(0)$ are observed and initial magnitude, respectively.
Magnitude is related to intensity (I) as:
\begin{equation}
m_{\lambda} = 2.5 \log (I_{\lambda}) + C,
\end{equation}
where $c$ is a constant which depends on photometric system that is being used.
Optical depth, $\tau_{\lambda}$, is defined by ratio of observed and initial intensity of a source as:
\begin{equation}
\label{equ: extinction}
{\mathrm I}(\lambda) = {\mathrm I}_0(\lambda)\exp[-\tau_{\lambda}],
\end{equation}
where I$(\lambda)$ is observed intensity in wavelength $\lambda$ and I$_0(\lambda)$ is intensity of light before passing through dust.
Therefore, the optical depth and extinction can be converted to one an other by $\tau_{\lambda} = 1.086 \mathrm{A}_{\lambda}$. 
The extinction also depends on the grain size and extinction cross section.
For measuring SFR using various wavebands, decreasing of the intensity of radiation must be calculated and corrected for each wavelength; otherwise, there will be an underestimation of SFR.

@@

\section{Measuring the star formation rate in galaxies} 
\label{sec: sfr_intro}
Understanding the formation of stars leads to better understanding of galaxies' formation and evolution. 
Characterisation of the star formation processes such as star formation rate (SFR) and the stellar initial mass function (IMF) is necessary in examining galaxies' structure formation~\citep{McKee07}. 
Measuring the SFR is not trivial and depends on a galaxy's morphology, metallicity, IMF, observational spatial resolution, and other properties. 
There is a large number of review papers on how stars form and how their formation is traced. 
From a theoretical perspective, one can refer to the classic picture of the theory of star formation as reviewed by \cite{Shu87} and more recently by~\cite{McKee07}. 
From an observational standpoint, star formation is discussed by many authers \citep[e.g.][and references therein]{Kennicutt98b, Kewley02, Calzetti13, Boquien10, Kennicutt12}.

@@

Another single-band SFR indicator is the emission from hydrogen recombination lines. 
Ionizing photons emitted from young massive stars ionize the surrounding gas. Hydrogen recombination line emission, such as the Balmer series lines of H${\alpha}$ ($0.6563 \mu$m) and H${\beta}$ ($0.4861 \mu$m), which are located in the optical wavelength range, are among the most traditional SFR indicators~\citep{Kennicutt98a}. 
The relationship between the intensity of a hydrogen recombination line and the ionizing photon rate for a nebula is derived using quantum mechanics. 
The assumption is that the nebula must be optically thick to ionizing photons~\citep{Osterbrock06}.
Being optically thick means that almost all transitions more energetic than Ly${\alpha}$ absorb and re-emit via Ly${\alpha}$ and longer wavelengths.
This is why the H${\alpha}$ emission line strength is greater in optically thick environments. The relation between the SFR, the luminosity of the \halpha emission line, and the ionizing photon rate is~\citep[e.g.,][]{Osterbrock06, Kennicutt98b}:
\begin{align}
\label{equ: halpha}
SFR(H\alpha) = 5.5 \times 10^{-42}L(H\alpha) \\
                     = 7.4 \times 10^{-54}Q(H^{\circ})
\end{align}
where SFR(\halpha) is in M$_{\odot}$~yr$^{-1}$, L(\halpha) is in erg~s$^{-1}$, and Q(H$^{\circ}$) is the ionizing photon rate in units of s$^{-1}$.
The constant on the right-hand side of Equ.~\ref{equ: halpha} is the resulting coefficient for electron temperature T$_{\mathrm{e}}=10000$~K and density n$_{\mathrm{e}}=100$~cm$^{-3}$ which is typical in the \hii~regions.
Dust extinction (Section~\ref{sec: ism_intro}) is the most important source of systematic error in calculating the SFR from hydrogen recombination lines.
The effects of dust must be measured and \halpha observations must be corrected for extinction (e.g. by adding lumincity at 24~$\mu$m (L(24~$\mu$m)) to account for dust emission) or this could lead to underestimating the SFR~\citep{Kennicutt98b}.

@@

In this thesis, I present three projects that study the effects of galaxy properties on star formation.
I use UV to radio observations of both nearby and high-redshift galaxies, measure their physical properties, and using modern statistical methods, study their impact on SFR.
Chapter~\ref{ch: paper1} focuses on investigating star formation laws in the Andromeda galaxy (M31) on both local and global scales using hierarchical Bayesian analysis.
In addition to the Kennicutt-Schmidt law, I study the extended Schmidt law~\citep{Shi11} and the metallicity/star formation correlation~\citep{Krumholz09}.
I also show the effect on star formation laws by using different SFR and ISM gas tracers.
In Chapter~\ref{ch: paper3}, I explore nearby galaxies using an unsupervised data-mining method (the self-organizing map, or SOM).
I cluster observational data to derive quantities of spatially resolved regions in M31 and examine the physical properties of each cluster.
During this process, I find hidden structures in high-dimensional data space.
In Chapter~\ref{ch: paper2}, I move to more distant galaxies and apply the SOM algorithm to their spectral energy distributions.
I train networks using a set of galaxy SED templates covering the wavelength range from UV to IR and use them to classify the SEDs of a sample of 142 galaxies with $0.5 < z < 1$. 
Then I study the grouped properties of the classified galaxies.
I summarize these results and discuss potential future work and applications of the results of this thesis in Chapter~\ref{ch: summary}

>>>>

%ISM 1)Gas 2)dust
%There could be a galaxy without stars (i.e. dark galaxies~\citep[][and references therein]{Cantalupo12}), but there will never be a galaxy without gas. %: this is a very strong statement. Some galaxies, like dwarf ellipticals, are pretty gas-free (at least now). So qualify this a bit. done
Among observable objects in galaxies, gas has a crucial role in formation and evolution of galaxies.
Gas and dust in galaxies can be found in the space between stars.
This space is called the interstellar medium (ISM), and is full of low density gaseous clouds with neutral or ionized atoms and/or molecules, and microscopic dust grains.
The gas and dust in the ISM are heated by the interstellar radiation field and cooled through a variety of line and continuum processes which usually depend on the local physical conditions. 
The effect of the ISM on stellar formation is undeniable; it provides the raw material for the formation of stars~\citep[e.g.][]{Kennicutt08,Bigiel08}.
Studying the interstellar medium is not only essential to understanding the formation of stars, but is also  necessary for interpretation of stellar evolution due to fact that stars release their material into ISM when they reach the end of their evolutionary track.

@@

The molecular clouds are surrounded by clouds of atomic gas~\citep{Kennicutt12}, which are easily traceable by 21-cm emission.
Hydrogen atoms in the ISM (excluding the regions close to hot stars, see below) are in their ground state, which is the state of lowest energy.
Due to a coupling between the total angular momentum of the electron and the angular momentum (spin) of the nucleus, the ground state of hydrogen atom splits into two states that are separated in energy by an amount of 9.4E-25~J.
This splitting is referred to as the hyperfine structure. 
The electron can be in either of the two aforementioned states. 
These states are very stable and the transition between them is forbidden, with a transition rate of $2.5\times10^{-15}\mathrm{s}^{-1}$.
This means that one would expect this transition to naturally happen once every ten million years.
%The electron and proton spins in the ground state can be parallel (i.e. both spin up) or anti-parallel (i.e. the proton's spin is up and the electron's spin is down or vice versa). 
%The energy of the anti-parallel mode is slightly less than the parallel mode.
%Since atoms always tend to be in the state with lowest energy possible, electrons in the parallel mode have a tendency to flip to the anti-parallel mode. 
%However, the energy difference between these two states is very small and it takes millions of years before the transition happens.
However, the large amounts of hydrogen atoms in these atomic clouds compensate for the rarity of the transition and at any given time, there are enough hydrogen atoms to emit the 21-cm radiation. 
Observation of the \hi~atoms is specifically necessary for understanding physical properties and dynamics of the ISM, which leads to understanding the star formation process~\citep{Walter08}.

@@

Dust has an insignificant effect on the mass of the ISM, but it plays crucial roles in the ISM's evolution.
In spiral galaxies, dust grains are located in cold regions ($\sim$30~K) and empirically found to have a power-law size distribution.
The source of energy for dust thermal emission is heating from stars, and the shape of the continuum depends on size of the grain.
Mid-infrared emission from dust grains is mainly dominated by PAHs heated by evolved stellar population~\citep{Smith07a} or recently formed intermediate-mass young stars~\citep{Peeters04}.
Large grains that are either heated by light from star-forming regions or by the interstellar radiation field from the total stellar population emit most of their light in far-infrared~\citep[e.g.][]{Calapa14, lu14}
Dust is the main source of extinction and reddening of starlight (see Sec.\ref{sec: extinction} for more information).

@@

Extinction happens when there is a combination of both absorption and scattering of radiation by dust.
This effect grows inversely with wavelength.
%Extinction can be defined as a reduction of the original intensity caused by dust:
Extinction is quantified as the difference between observed and intrinsic magnitudes of an object at a specific wavelength ($\lambda$):
\begin{equation}
m_{\lambda} - m_{\lambda}(0) = \mathrm{A}_{\lambda},
\end{equation}
where $\mathrm{A}_{\lambda}$ is the extinction, and $m_{\lambda}$ and $m_{\lambda}(0)$ are the observed and intrinsic magnitudes, respectively.
Magnitude is related to intensity ($I$) as:
\begin{equation}
m_{\lambda} = 2.5 \log (I_{\lambda}) + C,
\end{equation}
where $C$ is a constant which depends on the photometric system that is being used.
Optical depth, $\tau_{\lambda}$, is defined as the ratio of observed and intrinsic intensity for a source as:
\begin{equation}
\label{equ: extinction}
{\mathrm I}(\lambda) = {\mathrm I}_0(\lambda)\exp[-\tau_{\lambda}],
\end{equation}
where I$(\lambda)$ is the observed intensity at wavelength $\lambda$ and I$_0(\lambda)$ is the intensity of light before it passes through the extincting dust.
Therefore, the optical depth and extinction can be converted to one another by $\tau_{\lambda} = 1.086 \mathrm{A}_{\lambda}$. 
The extinction also depends on the grain size and extinction cross section.
For measuring SFR using various wavebands, the decrease in the intensity of radiation must be calculated and corrected for each wavelength; otherwise, there will be an underestimation of SFR.

@@

\section{Measuring the star formation rate in galaxies} 
\label{sec: sfr_intro}
Understanding the formation of stars leads to better understanding of galaxies' formation and evolution. 
Characterisation of the star formation processes such as star formation rate (SFR) and the stellar initial mass function (IMF) is necessary in examining galaxies' structure formation~\citep{McKee07}. 
Measuring the SFR is not trivial and depends on a galaxy's morphology, metallicity, IMF, observational spatial resolution, and other properties. 
There is a large number of review papers on how stars form and how their formation is traced. 
From a theoretical perspective, one can refer to the classic picture of the theory of star formation as reviewed by \cite{Shu87} and more recently by~\cite{McKee07}. 
From an observational standpoint, star formation is discussed by many authors \citep[e.g.][and references therein]{Kennicutt98b, Kewley02, Calzetti13, Boquien10, Kennicutt12}.

@@

Another single-band SFR indicator is the emission from hydrogen recombination lines. 
Ionizing photons emitted from young massive stars ionize the surrounding gas. Hydrogen recombination line emission, such as the Balmer series lines of H${\alpha}$ ($0.6563 \mu$m) and H${\beta}$ ($0.4861 \mu$m), which are located in the optical wavelength range, are among the most traditional SFR indicators~\citep{Kennicutt98a}. 
The relationship between the intensity of a hydrogen recombination line and the ionizing photon rate for a nebula is derived using quantum mechanics. 
The assumption is that the nebula must be optically thick to ionizing photons~\citep{Osterbrock06}.
Being optically thick means that almost all transitions more energetic than Ly${\alpha}$ absorb and re-emit via Ly${\alpha}$ and longer wavelengths.
This is why the H${\alpha}$ emission line strength is greater in optically thick environments. The relation between the SFR, the luminosity of the \halpha emission line, and the ionizing photon rate is~\citep[e.g.,][]{Osterbrock06, Kennicutt98b}:
\begin{align}
\label{equ: halpha}
SFR(H\alpha) = 5.5 \times 10^{-42}L(H\alpha) \\
                     = 7.4 \times 10^{-54}Q(H^{\circ})
\end{align}
where SFR(\halpha) is in M$_{\odot}$~yr$^{-1}$, L(\halpha) is in erg~s$^{-1}$, and Q(H$^{\circ}$) is the ionizing photon rate in units of s$^{-1}$.
The constant on the right-hand side of Equ.~\ref{equ: halpha} is the resulting coefficient for electron temperature T$_{\mathrm{e}}=10000$~K and density n$_{\mathrm{e}}=100$~cm$^{-3}$ which is typical in the \hii~regions.
Dust extinction (Section~\ref{sec: ism_intro}) is the most important source of systematic error in calculating the SFR from hydrogen recombination lines.
The effects of dust must be measured and \halpha observations must be corrected for extinction (e.g. by adding luminosity at 24~$\mu$m (L(24~$\mu$m)) to account for dust emission) or this could lead to underestimating the SFR~\citep{Kennicutt98b}.

@@

In this thesis, I present three projects that study the effects of galaxy properties on star formation.
I use UV to radio observations of both nearby and high-redshift galaxies, measure their physical properties, and using modern statistical methods, study their impact on SFR.
Chapter~\ref{ch: paper1} focuses on investigating star formation laws in the Andromeda galaxy (M31) on both local and global scales using hierarchical Bayesian analysis.
In addition to the Kennicutt-Schmidt law, I study the extended Schmidt law~\citep{Shi11} and the metallicity/star formation correlation~\citep{Krumholz09}.
I also show the effect on star formation laws by using different SFR and ISM gas tracers.
In Chapter~\ref{ch: paper3}, I explore nearby galaxies using an unsupervised data-mining method (the self-organizing map, or SOM).
I cluster observational data to derive quantities of spatially resolved regions in M31 and examine the physical properties of each cluster.
During this process, I find hidden structures in a high-dimensional data space.
In Chapter~\ref{ch: paper2}, I move to more distant galaxies and apply the SOM algorithm to their spectra.
I train networks using a set of galaxy spectral templates covering the wavelength range from UV to IR and use them to classify the spectra of a sample of 142 galaxies with $0.5 < z < 1$. 
Then I study the grouped properties of the classified galaxies.
I summarize these results and discuss potential future work and applications of the results of this thesis in Chapter~\ref{ch: summary}

### 2016-08-31 version0.0/summary.tex
Changing MHz to J

It has been well established that to form stars, gas is the main ingredient.
However, the relation between SFR and different tracers of gas mass (atomic, molecular, or total gas) changes in different type of galaxies.
Relations between stellar mass, metallicity and SFR are not clear and there are fewer studies of these than of the relation between SFR and gas mass.
The dependence of SFR on other properties of galaxies such as morphology and dust mass have been tested as well, but there is no SFR law that considers all of the above quantities together.
The Kennicutt-Schmidt law ~\citep{Schmidt59, Kennicutt98b} was the first empirical star formation law, suggesting that SFR and molecular gas have a logarithmic correlation with each other. 
However, after many years and studies, there is still an ongoing question of whether it is a universal law or not.
\citet{Shetty13} showed that, besides the physical and environmental effects, fitting methods also change our perspective of the K-S law.
Extended version of the K-S law were introduced by adding the effect of stars (extended Schmidt law; introduced by ~\citealt{Shi11}) or metallicity (Krumholz law; introduced by ~\citealt{Krumholz09}).
Compared to the K-S law, the extended Schmidt law and Krumholz law are relatively recently introduced and still need to be tested with diverse statistical methods on different scales (local and global), with various morphological types and in both nearby and high-redshift galaxies.

>>>>

It has been well established that to form stars, gas is the main ingredient.
However, the relation between SFR and different tracers of gas mass (atomic, molecular, or total gas) changes in different type of galaxies.
Relations between stellar mass, metallicity and SFR are not clear and there are fewer studies of these than of the relation between SFR and gas mass.
The dependence of SFR on other properties of galaxies such as morphology and dust mass have been tested as well, but there is no SFR law that considers all of the above quantities together.
The Kennicutt-Schmidt law~\citep{Schmidt59, Kennicutt98b} was the first empirical star formation law, suggesting that SFR and molecular gas have a logarithmic correlation with each other. 
However, after many years and studies, there is still an ongoing question of whether it is a universal law or not.
\citet{Shetty13} showed that, besides the physical and environmental effects, fitting methods also change our perspective of the K-S law.
Extended version of the K-S law were introduced by adding the effect of stars (extended Schmidt law; introduced by~\citealt{Shi11}) or metallicity (Krumholz law; introduced by~\citealt{Krumholz09}).
Compared to the K-S law, the extended Schmidt law and Krumholz law are relatively recently introduced and still need to be tested with diverse statistical methods on different scales (local and global), with various morphological types and in both nearby and high-redshift galaxies.
